---
title: "Data reanalysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(googlesheets) #Go to google sheets
gs<- gs_title("COXdata")
gs
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rs<-gs_read(ss=gs,ws="brain_bodymass")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)

Scalingplot<-ggplot(rs, aes(x = log(estimated_body_mass_mg), y = log(brain_mass_µg), colour = species)) + geom_point()+ geom_smooth(method="lm", fill=NA)+ scale_color_manual(values = c("purple", "dark green"))

SP<-Scalingplot + xlab("ln(body mass(mg)") + ylab("ln(brain mass(ug)") 

SP
```
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(readxl)
ds<-"C:/Users/--/Desktop/R data reanalysis/COX ms data for Dryad.xlsx"
rs2<-read_excel(ds, sheet = 1)

library(ggplot2)

Scalingplot2<-ggplot(rs2, aes(x = log(estimated_body_mass_mg), y = log(brain_mass_µg), colour = species)) + geom_point()+ geom_smooth(method="lm", fill=NA)+ scale_color_manual(values = c("purple", "dark green"))

SP2<-Scalingplot2 + xlab("ln(body mass(mg)") + ylab("ln(brain mass(ug)") 

SP2

![] (https://github.com/ZachCoto/Data-Reanalysis/blob/master/Recreation%20of%20Figure%202%20from%20Kamhi%20et%20al%202016.png)
```

